\documentclass[a4paper,10pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=0.5in]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}

% Custom Colors
\definecolor{primary}{RGB}{0, 0, 0}

% Section Formatting
\titleformat{\section}{\large\bfseries\uppercase}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{5pt}

% Custom command for aligned rows
\newcommand{\resumeHeaderLine}[2]{
  \noindent\begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
    \textbf{#1} & #2 \\
  \end{tabular*}\vspace{-2pt}
}

\begin{document}

% --- HEADER ---
\begin{center}
    {\Huge \textbf{Abhay Sharma}} \\
    \vspace{4pt}
    Senior Backend Developer \\
    \vspace{2pt}
    Faridabad, Haryana, India $\cdot$ +91 7210089184 $\cdot$ \href{mailto:whoabhaysharma@gmail.com}{whoabhaysharma@gmail.com} \\
    \vspace{2pt}
    \href{https://linkedin.com/in/whoabhaysharma}{linkedin.com/in/whoabhaysharma} $\cdot$ \href{https://github.com/whoabhaysharma}{github.com/whoabhaysharma} $\cdot$ \href{https://abhaysharma.pages.dev}{portfolio}
\end{center}

% --- SUMMARY ---
\section{Professional Summary}
Senior Backend Developer with 6+ years of experience specializing in scalable backend systems. Expert in Node.js, Express.js, and TypeScript, complemented by extensive experience building high-performance architectures. Proven ability to lead projects end-to-end—from database design to API implementation and production deployment.

% --- SKILLS ---
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, labelsep=0.5em]
    \item \textbf{Backend/Integration:} Node.js, Express.js, NestJS, Prisma, RESTful APIs, GraphQL, Microservices, Redis, PostgreSQL, MongoDB, WhatsApp Cloud API
    \item \textbf{Frontend:} JavaScript (ES6+), TypeScript, React.js, Next.js (Basic knowledge)
    \item \textbf{Tools:} Git, GitHub, Docker, Kubernetes, AWS, CI/CD, Postman
\end{itemize}

% --- EXPERIENCE ---
\section{Professional Experience}

\resumeHeaderLine{Techcrumb Solution Pvt. Ltd. (Dilogs.com)}{Faridabad, India}
\textit{Senior Backend Developer} \hfill Oct 2023 – Present
\begin{itemize}[noitemsep, topsep=0pt]
    \item Spearheaded the end-to-end backend architecture for an AI-powered video ad creation platform.
    \item Designed and implemented scalable RESTful APIs to handle heavy video processing workloads.
    \item Optimized database queries and schema design to ensure low-latency data retrieval for the video editor.
    \item Managed cloud infrastructure and deployment pipelines for high availability.
\end{itemize}

\vspace{4pt}

\resumeHeaderLine{Techcrumb Solution Pvt. Ltd. (Performoo.com)}{Faridabad, India}
\textit{Backend Developer} \hfill June 2020 – Oct 2023
\begin{itemize}[noitemsep, topsep=0pt]
    \item Architected and built the core backend services for a comprehensive ad-unit and campaign management platform using Node.js and Express.
    \item Developed a high-throughput real-time analytics engine to capture and process engagement metrics.
    \item Optimized API performance for the core video ad player, reducing latency and ensuring rapid content delivery.
    \item Collaborated with frontend teams to define API contracts and ensure seamless data integration.
\end{itemize}

\vspace{4pt}

\resumeHeaderLine{Techcrumb Solution Pvt. Ltd.}{Faridabad, India}
\textit{Backend Developer Intern} \hfill Nov 2019 – Apr 2020
\begin{itemize}[noitemsep, topsep=0pt]
    \item Assisted in optimizing backend API performance for an ad player platform.
    \item Worked on database migrations and query optimization.
\end{itemize}

% --- PROJECTS ---
\section{Key Projects}

\resumeHeaderLine{QuixHR.com | Leave Management SaaS}{Node.js, Express.js, Prisma}
\begin{itemize}[noitemsep, topsep=0pt]
    \item Developed a multi-tenant leave management system for automated employee requests, approvals, and HR tracking.
    \item Built scalable database schemas using Prisma to handle organizational hierarchies and multi-company data isolation.
    \item Implemented secure authentication and authorization mechanisms.
\end{itemize}

\vspace{4pt}

\resumeHeaderLine{Gyms24.in | Gym Booking Platform}{Node.js, PostgreSQL, WhatsApp API}
\begin{itemize}[noitemsep, topsep=0pt]
    \item Engineered backend services for a gym discovery platform utilizing WhatsApp Cloud API.
    \item Implemented transactional logic for booking and membership verification.
    \item Integrated a secure QR code verification system for gym owners to scan and verify membership status at entry points.
\end{itemize}

% --- EDUCATION ---
\section{Education}
\resumeHeaderLine{Echelon Institute of Technology}{Faridabad, India}
\textit{B.Tech., Computer Science \& Engineering (GPA: 7.4/10)} \hfill 2016 – 2020

% --- INTERESTS ---
\section{Interests}
Watching sci-fi movies, creating innovative solutions for daily life problems, and listening to music.

\end{document}
