\documentclass[a4paper,10pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=0.5in]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}

% Custom Colors
\definecolor{primary}{RGB}{0, 0, 0}

% Section Formatting
\titleformat{\section}{\large\bfseries\uppercase}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{5pt}

% Custom command for aligned rows
\newcommand{\resumeHeaderLine}[2]{
  \noindent\begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
    \textbf{#1} & #2 \\
  \end{tabular*}\vspace{-2pt}
}

\begin{document}

% --- HEADER ---
\begin{center}
    {\Huge \textbf{Abhay Sharma}} \\
    \vspace{4pt}
    Senior Frontend Developer \\
    \vspace{2pt}
    Faridabad, Haryana, India $\cdot$ +91 7210089184 $\cdot$ \href{mailto:whoabhaysharma@gmail.com}{whoabhaysharma@gmail.com} \\
    \vspace{2pt}
    \href{https://linkedin.com/in/whoabhaysharma}{linkedin.com/in/whoabhaysharma} $\cdot$ \href{https://github.com/whoabhaysharma}{github.com/whoabhaysharma} $\cdot$ \href{https://abhaysharma.pages.dev}{portfolio}
\end{center}

% --- SUMMARY ---
\section{Professional Summary}
Senior Full Stack Developer with 4+ years of experience specializing in high-performance SaaS platforms. Expert in React.js, Next.js, and TypeScript, complemented by extensive experience building scalable backend architectures with Node.js and Express. Proven ability to lead projects end-to-end—from initial UI/UX design in Figma to full-stack implementation and production deployment.

% --- SKILLS ---
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, labelsep=0.5em]
    \item \textbf{Frontend:} JavaScript (ES6+), TypeScript, React.js, Next.js, Redux, HTML5, CSS3, Tailwind CSS, Webpack
    \item \textbf{Design:} Figma (UX/UI Design), Responsive Design, Prototyping
    \item \textbf{Backend/Integration:} Node.js, Express.js, Prisma, RESTful APIs, WhatsApp Cloud API
    \item \textbf{Tools:} Git, GitHub, Docker, AWS, Vercel, Netlify
\end{itemize}

% --- EXPERIENCE ---
\section{Professional Experience}

\resumeHeaderLine{Techcrumb Solution Pvt. Ltd. (Dilogs.com)}{Faridabad, India}
\textit{Senior Frontend Developer} \hfill Oct 2024 – Present
\begin{itemize}[noitemsep, topsep=0pt]
    \item Spearheaded the end-to-end UX/UI design and frontend development for an AI-powered video ad creation platform.
    \item Designed the entire user interface from scratch in Figma, focusing on a seamless workflow for generating long and short-form video content.
    \item Developed a custom web-based video editor allowing users to merge, trim, and combine multiple AI-generated ads into a single cohesive video campaign.
\end{itemize}

\vspace{4pt}

\resumeHeaderLine{Techcrumb Solution Pvt. Ltd. (Performoo.com)}{Faridabad, India}
\textit{Frontend Developer} \hfill June 2021 – Oct 2024
\begin{itemize}[noitemsep, topsep=0pt]
    \item Architected and built a comprehensive ad-unit and campaign management platform from scratch using React, Webpack, and Next.js.
    \item Engineered an internal framework to render high-engagement rich media formats (including full-screen overlays and interactive banners) while capturing detailed real-time analytics.
    \item Maintained and optimized a core video ad player, ensuring low-latency playback and cross-browser compatibility.
    \item Collaborated closely with the design team to translate complex creative requirements into functional, high-performance components.
\end{itemize}

\vspace{4pt}

\resumeHeaderLine{Techcrumb Solution Pvt. Ltd.}{Faridabad, India}
\textit{Frontend Developer Intern} \hfill Nov 2020 – Apr 2021
\begin{itemize}[noitemsep, topsep=0pt]
    \item Optimized asset delivery for an ad player platform and enhanced UI responsiveness.
\end{itemize}

% --- PROJECTS ---
\section{Key Projects}

\resumeHeaderLine{QuixHR.com | Leave Management SaaS}{Next.js, Express.js, Prisma}
\begin{itemize}[noitemsep, topsep=0pt]
    \item Developed a multi-tenant leave management system for automated employee requests, approvals, and HR tracking.
    \item Built scalable database schemas using Prisma to handle organizational hierarchies and multi-company data isolation.
\end{itemize}

\vspace{4pt}

\resumeHeaderLine{Gyms24.in | Gym Booking Platform}{React, Node.js, WhatsApp API}
\begin{itemize}[noitemsep, topsep=0pt]
    \item Engineered a gym discovery and booking platform utilizing the WhatsApp Cloud API for direct user communication and lead management.
    \item Integrated a secure QR code verification system for gym owners to scan and verify membership status at entry points.
\end{itemize}

% --- EDUCATION ---
\section{Education}
\resumeHeaderLine{Echelon Institute of Technology}{Faridabad, India}
\textit{B.Tech., Computer Science \& Engineering (GPA: 7.4/10)} \hfill 2017 – 2021

% --- INTERESTS ---
\section{Interests}
Watching sci-fi movies, creating innovative solutions for daily life problems, and listening to music.

\end{document}